Enforced Invariant Confluence

### 2018-04-01 doc/paper/sections/introduction.tex
Small tweak to intro.

Then, we use these conditions to design a general-purpose interactive
invariant-confluence decision procedure. Users iteratively interact with the
decision procedure, eliminating unreachable states from the invariant and
moving towards the conditions under which invariant-closure and
invariant-confluence are equivalent. Meanwhile, the decision-procedure
generates example reachable and unreachable states which help the user
recognize patterns that describe reachability. We also leverage our intuitions
about reachability to develop a new sufficient condition for
invariant-confluence, dubbed merge-reducibility. Merge-reducibility covers some
cases that are not covered by invariant-closure, and it can be automatically
checked without any user interaction.

>>>>

Then, we use these conditions to design a general-purpose interactive
invariant-confluence decision procedure. Users iteratively interact with the
decision procedure, eliminating unreachable states from the invariant, moving
towards the conditions under which invariant-closure and invariant-confluence
are equivalent. Meanwhile, the decision-procedure generates example reachable
and unreachable states which help the user recognize patterns that describe
reachability. We also leverage our intuitions about reachability to develop a
new sufficient condition for invariant-confluence, dubbed merge-reducibility.
Merge-reducibility covers some cases that are not covered by invariant-closure,
and it can be automatically checked without any user interaction.
